\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\begin{document}

\section*{Progress Report 15}
Stuart, Walt, Dan

%% tasks and task owners for roughly the next 24 hours
\section*{Next Goals and Deliverables}
\begin{itemize}
    \item Modify network layer to let clients act as routers and have dynamic routing table updates. - Stuart
    \item Implement Pong game using new packet interpretation system. - Walt
    \item Develop experiments and benchmark tests - Dan
    \item Write paper - group
    
\end{itemize}

%% Section enumerating progress from the previous day. Items people were responsible for in the last progress report must appear. Additional tasks that the group agreed to add since the last progress report may be presented here.
\section*{Previous Goals and Deliverables}
\begin{itemize}
    \item Abstract packet creation to packet struct (IN PROGRESS)- Walt
    \item Create packet data interpretation system (IN PROGRESS)- Stuart
    \item Create pong game (IN PROGRESS)- Stuart
    \item Generalize network layer to accept any application and send to any port (IN PROGRESS)- Walt/Dan
    \item Implement error packet and handle no stop sequence (TRIAGED)- group
    \item Run expiriments on baud rates, and profile program to determine where bottlenecks are. (IN PROGRESS)- group
    \item Build queue for sending when keyboard spammed (TRIAGED)- Dan
    \item Begin writing paper - (IN PROGRESS) group
\end{itemize}

%% Sections above should be short bullets. Longer free form discussion of information from above goes here. These should still be short! More that a couple sentences and the discussion is better suited as a results write-up, appendix, or design document.
\section*{Discussion}
\begin{itemize}
    \item We are in a tough spot at the moment because we are trying to make big changes to different parts of the network at once. We are both modifying
    the network routing process and protocol at the same time as we are implementing a more complex application.
    \item As we are not done with what we had been hoping to accomplish, we have also fallen a bit behind on our paper. We are going to start
    writing it with the deliverables we have now, but we hope to expand on some of the features we've already implemented to have a more finished
    network.
    \item Since there are still a lot of ways we could improve our project, we are having to be decisive about what we want to spend time on. For now,
    we have decided that making a more secure network layer is important, along with having a unique application that we can present to the group.    
\end{itemize}

%% The appendix pages go here if there are any...
%\section*{Appendix}
\end{document}