\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\begin{document}

\section*{Progress Report 14}
Stuart, Walt, Dan

%% tasks and task owners for roughly the next 24 hours
\section*{Next Goals and Deliverables}
\begin{itemize}
    \item Abstract packet creation to packet struct - Walt
    \item Create packet data interpretation system - Stuart
    \item Create pong game - Stuart
    \item Generalize network layer to accept any application and send to any port - Walt/Dan
    \item Implement error packet and handle no stop sequence - group
    \item Run expiriments on baud rates, and profile program to determine where bottlenecks are. - group
    \item Build queue for sending when keyboard spammed - Dan
    \item Begin writing paper - group
\end{itemize}

%% Section enumerating progress from the previous day. Items people were responsible for in the last progress report must appear. Additional tasks that the group agreed to add since the last progress report may be presented here.
\section*{Previous Goals and Deliverables}
\begin{itemize}
    \item Generalize packet creation to packet struct (IN PROGRESS) - Walt
    \item Create packet data interpretation system (IN PROGRESS) - Stuart
    \item Create pong game (IN PROGRESS) - Stuart
    \item Abstract packet creation to packet struct (IN PROGRESS) - Walt
    \item Generalize network layer to accept any application and send to any port (IN PROGRESS) - Walt/Dan
    \item Implement error packet and handle no stop sequence (IN PROGRESS) - group
    \item Run expiriments on baud rates, and profile program to determine where bottlenecks are. (IN PROGRESS) - group
\end{itemize}

%% Sections above should be short bullets. Longer free form discussion of information from above goes here. These should still be short! More that a couple sentences and the discussion is better suited as a results write-up, appendix, or design document.
\section*{Discussion}
\begin{itemize}
    \item Today we did not get a ton done due to most of class being spent learning from David Z of CC ITS about CC's netowork infra and busy schedules
    following class. Tomorrow we will pick things up.
    \item Walt managed to debug most the chat application Dan and him developed earlier in the week. We have yet to test these revisions on the pis, but we
    feel confident it will prevent the listening errors we were running into. If successful, this will mark our first app that functions with the network layer.
    \item As we prepare to write our paper, we are going to do code cleanup and various load testing experiments to evaluate the strengths and weaknesses of
    our network.
    \item Stuart is continuing to develop his pong application. We are hoping to have latency to a minimum by the time this program is ready for testing.
\end{itemize}

%% The appendix pages go here if there are any...
%\section*{Appendix}
\end{document}