\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\begin{document}

%% tasks and task owners for roughly the next 24 hours
\section*{Next Goals and Deliverables}
\begin{itemize}
\item Continue research into timing, error detection/correction - Group
\item Max speed and size experiment - Stuart/Walt
\item Two pi clock comparison experiment - Dan/Walt
\item Waveform v. serialized approach research and evaluation - Group
\item Make bash script command for mounting USB on the Pi - Walt
\end{itemize}

%% Section enumerating progress from the previous day. Items people were
responsible for in the last progress report must appear. Additional tasks that the
group agreed to add since the last progress report may be presented here.
\section*{Previous Goals and Deliverables}
\begin{itemize}
    \item Light experiment (DONE) - pushed by Stuart (/src/test.c)
    \item Read basic networking background material (done), going to continue this more in-depth as development continues (see new directory: /research)
    \item Timing, clocks, etc, (partial) - Stuart (more of a group responsibility now) 
    \item Error detection/correction research (partial) - Dan (more of a group responsibility now)
    \item Update project outline - next update Thursday
    \item Group name decision: We are "Bitties"
    \item Uploaded updated pin mapping for important GPIOs (DONE) - Dan (/progress_reports/day2/Pin outs NIC-Pi 3 B+ - Important Pin Outs.csv)
\end{itemize}

%% Sections above should be short bullets. Longer free form discussion of
information from above goes here. These should still be short! More that a couple
sentences and the discussion is better suited as a results write-up, appendix, or
design document.
\section*{Discussion}
\begin{itemize}
\item After getting our footing connecting the Pi and the NIC, we worked on a light experiment. After some
painful troubleshooting, we discovered errors in our pin mapping from yesterday, and then managed to make all
transmitter lights turn on and off (see how we did it in test.c in /experiments).
\item We have stumbled upon multiple approaches to developing our link layer when it comes to dealing with timing and error detection/correction. 
Before we decide on which approach is best, we want to do some basic experiments (max speed and size, two pi clock comparison) to gain a better understanding
of the problems (timing, bit flipping) that were outlined today in discussion.
\item We are curious about creating a waveform for sending a packet from one pi to another because this approach might not be as affected by timing errors as NRZ. This is
a topic of discussion we will continue tomorrow and potentially devise an experiment for if we deem it as a viable option. 
\item Interfacing with the pi and a USB is tedious. We will write a bash script command tomorrow to make this process more pleasent. 
\end{itemize}

%% The appendix pages go here if there are any...
%\section*{Appendix}
\end{document}
