\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\begin{document}

%% tasks and task owners for roughly the next 24 hours
\section*{Next Goals and Deliverables}
\begin{itemize}
\item Pulse experiment - Danielle
\item Continue NRZ research - Laurie/Alex
\item NRZ experiment 1 - Laurie/Alex
\item Error detection/correction - Deferred
\item Update project outline - next update Thursday
\end{itemize}

%% Section enumerating progress from the previous day. Items people were
responsible for in the last progress report must appear. Additional tasks that the
group agreed to add since the last progress report may be presented here.
\section*{Previous Goals and Deliverables}
\begin{itemize}
\item Setup private github repo (DONE) - Danielle (ccdellswor/2024b2networks)
\item Commit README.md with practices (DONE) - Day 1 team meeting, commit by Alex
\item HW Pin Mapping (DONE) - all, commit by Danielle
\item Research NRZ encoding (partial) - bibtex additions by all (final/bib.tex)
\item Research error detection (not started) - agreed to defer until we have some
experience with the HW
\item Draft project outline - commit by Laurie
\end{itemize}

%% Sections above should be short bullets. Longer free form discussion of
information from above goes here. These should still be short! More that a couple
sentences and the discussion is better suited as a results write-up, appendix, or
design document.
\section*{Discussion}
\begin{itemize}
\item Team generated a pretty highlevel outline for what needs to be done during
the 3 week project timeline. This will help us to keep track of how our daily
targets align with the higher level weekly milestones expected for the course.
\item Initial investigation into error detection requires bits... not sure how to
send even a single bit yet, so this research has been deferred. This may be a
mistake since we'll need to know this shortly after bits start being sent (the NICs
are known to suffer from substantial noise/crosstalk).
\item Pulse experiment - Using a single node toggle tx on/off. Verify that rx
matches tx and generate some timing estimates for how fast toggling can be
detected. Will commit code and short results write up to repo; should give a sense
of an upperbound on bps.
\item Continue NRZ research - Not sure that we understand it yet. Will produce
pseudocode for the NRZ logic to implement and think through in detail.
\item NRZ Experiment 1 - Produce and commit C code that tries to send/recv 4 bit
patterns using a single node. This will build on the understanding gained
implementing the Pulse Experiment. Will try to get to running the experiment today
but expect this won't be ready/able to be run until tomorrow.
\end{itemize}

%% The appendix pages go here if there are any...
%\section*{Appendix}
\end{document}
